Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-09 paper/paper.tex
features example

\newcommand{\feat}[1]{\textsmaller[.5]{\textsf{#1}}} % code for a feature group
\newcommand{\textnl}{\textsl}

@@

\subsection{Motivation}
While some of the features were used in the works surveyed in
\Sref{sec:literature}, many are novel, and are inspired by the
features used to identify translationese by \citet{vered:noam:shuly}.
We begin by motivating our choice of features.

@@

\subsection{Main Features}
\label{sec:mainfeats}
First, we use the following four feature types as the core of our
model.  Whenever counts are mentioned, we use the log of the count as
the feature.  We report the accuracy of using each feature type, in
isolation, on the training set.

>>>>

\newcommand{\feat}[1]{\textsmaller[.5]{\textsf{#1}}} % code for a feature group
\newcommand{\featstr}[1]{\textsmaller[.5]{\verb|#1|}} % full feature name
\newcommand{\textnl}{\textsl}

@@

\subsection{Motivation}
While some of the features were used in the works surveyed in
\Sref{sec:literature}, many are novel, and are inspired by the
features used to identify translationese by \citet{vered:noam:shuly}.
We begin by motivating our choice of features, many of which are illustrated in \fref{fig:german} for an example sentence.

\begin{figure*}\centering\small
Firstly the employers live more savely because they are going to have more money to spend for luxury .\\[10pt]

\begin{tabular}{p{6em}p{15em}p{15em}}
 & \multicolumn{1}{c}{\bf Presence} & \multicolumn{1}{c}{\bf Considered alternatives/edits} \\
\hline
\bf Characters & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"CHAR_l_y_ "|:&$\log{2+1}$\\ \verb|"CharPrompt_P5_g_o_i"|:&$\log{1+1}$\\ \verb|"MFChar_e_ "|:&$\log{1+1}$\\ \verb|"Punc_period"|:&$\log{1+1}$\end{tabular}
 & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"DeleteP_p_."|:&$1.0$\\ \verb|"InsertP_p_,"|:&$1.0$\\ \verb|"MID:SUBST:v:f"|:&$\log{1+1}$\\ \verb|"SUBST:v:f"|:&$\log{1+1}$\end{tabular} \\
\hline
\bf Words & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"DocLen_"|:&$\log{19+1}$\\ \verb|"MeanWordRank"|:&$422.6$\\ \verb|"CohMarker_because"|:&$\log{1+1}$\\ \verb|"MostFreq_have"|:&$\log{1+1}$\\ 
\verb|"PosToken_last_luxury"|:&$\log{1+1}$\\ \verb|"Pronouns_they"|:&$\log{1+1}$\end{tabular}
 & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"MSP:safely"|:&$\log{1+1}$\\ \verb|"Match_p_to"|:&$0.5$\\ \verb|"Delete_p_to"|:&$0.5$\\ \verb|"Delete_p_are"|:&$1.0$\\ \verb|"Delete_p_because"|:&$1.0$\\ 
\verb|"Delete_p_for"|:&$1.0$\end{tabular} \\
\hline
\bf POS & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"POS_VBP_VBG_TO"|:&$\log{1+1}$\\ \verb|"POS_p_VBP_VBG_TO"|:&$0.059$\end{tabular} \\
\hline
\bf Words + POS & \smaller[.5]\begin{tabular}{@{}p{12em}p{5em}@{}}\verb|"VBP_VBG_to"|:&$\log{1+1}$\\ \verb|"FW__more RB"|:&$\log{1+1}$\end{tabular} \\
\hline
\end{tabular}

\caption{Some of the features extracted for an L1 German sentence.}\label{fig:german}
\end{figure*}

@@

\subsection{Main Features}
\label{sec:mainfeats}
First, we use the following four feature types as the core of our
model.  Whenever counts are mentioned, we use the log of the count-plus-one\nss{added: plus one} as
the feature.  We report the accuracy of using each feature type, in
isolation, on the training set.
